\section{Strategy}
This section outlines some strategies that can be useful for beginners who aren't sure what to prioritise when playing.

\subsection{Prioritise Waiting on More Sides}
In Mahjong and Rummy it's generally advised to \textit{wait} on two sides, that is to say it's safer to prioritise holding $\heartsuit 2\heartsuit 3$ than it is to hold $\heartsuit 1\heartsuit 2$---a so-called \textit{edge wait}.
The reason for this is simple: to complete a $\heartsuit 2\heartsuit 3$ run, you need either a $\heartsuit 1$ or a $\heartsuit 4$; but to complete $\heartsuit 1\heartsuit 2$ run, you need a $\heartsuit 3$. Edge waits thus have half as many options for you to draw upon as two-sided waits.

Playing with dominoes however, puts us in a rather unique situation: you can wait on more ``sides'' than just two.
This is due to the fact, that a tile can belong to up to three different sets simultaneously.
A { \domino <2>5 }, for example, can be in the suit of { \domino 2 }, the suit of { \domino 5 }, or even in the set of seven-sums.

So, suppose your hand contains of the following dominoes:
\begin{center}
{ \domino%
	^1^2^4\\
	v5v5v3\\%
}
\end{center}
This is effectively a \textit{quadruple}, or \textit{four-sided} wait, as any of the following would complete a meld:
\begin{center}
	{ \domino%
		^0\hspace{2mm}^3\hspace{2mm}^1\hspace{2mm}^7\\
		v5\hspace{2mm}v5\hspace{2mm}v6\hspace{2mm}v0\\%
	}
\end{center}

\subsection{Prioritise Sums}
Sums have two main benefits: They are easier to make royal, and they're harder to steal.

These two facts spring from the fact that sums are unevenly distributed. 
Sums near the middle are far more common than sums near the edges.

The sums near the edges have exactly one or two ways to be made into sets, and are thus impossible to steal.

For example, there's exactly one way to make a 4-sum:
\begin{center}
	{ \domino%
		^0^1^2\\
		v4v3v2\\%
	}
\end{center}

This sum is worth 12 points---2 for the sum, and 10 for the completion bonus---and it cannot be stolen! There are no tiles you can add to this meld to surround it and take it away.
However, due to there being exactly one way to make this sum, it is also very hard to make, so keep that in mind.